---
title: "Final report"
author: "Iris, Jette"
output:  pdf_document:

# Final knitted report 
This document brings everything together into one final, knitted report: the basic data inspection, the analyses/summaries, the regression analysis, and your conclusions, combined into a single PDF.

## Basic data inspection

```{r}
# Check for required packages, and install if missing
required_packages <- c("tidyverse", "here", "glue", "scales", "purrr")
missing_packages <- required_packages[!vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)]

if (length(missing_packages) > 0) {
  install.packages(missing_packages)
}

# Explicitly load all required packages, including newly introduced packages
library(tidyverse) # Includes ggplot2, dplyr, readr, stringr
library(here)      # Safe relative path resolution
library(glue)      # Tutorial technique: String interpolation
library(scales)    # Axis and text number formatting (e.g., comma labels)
library(purrr)     # Tutorial technique: Functional programming and loops (iwalk)

# Since data is already downloaded by makefile 

impressions <- read_csv(here("data", "raw", "impressions.csv"))
sessions <- read_csv(here("data", "raw", "sessions.csv"))
users <- read_csv(here("data", "raw", "users.csv"))
watch_events <- read_csv(here("data", "raw", "watch_events.csv"))

# Inspect 

datasets <- list(
  impressions = impressions,
  sessions = sessions,
  users = users,
  watch_events = watch_events
)

lapply(datasets, head)
lapply(datasets, names)
lapply(datasets, str)
lapply(datasets, summary)

# Cleaning of users
users_clean <- na.omit(users)

# Cleaning of watch_events
# Delete of raw data making clean file
watch_events_clean <- watch_events %>% select(-started_at_raw)

# Fixing started at and ended at

library(dplyr)

watch_events_clean <- watch_events_clean %>%
  mutate(
    started_at = as.POSIXct(started_at, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
    ended_at   = as.POSIXct(ended_at,   format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
  )
# Fixing missing data
watch_events_clean<- watch_events_clean %>% mutate(watch_seconds_calc = as.integer(as.numeric(difftime(ended_at, started_at, units = "secs"))))

watch_events_clean <- watch_events_clean %>% select(-watch_seconds) %>% rename(watch_seconds = watch_seconds_calc)

# Remove duplicate 'impression_id' (identical to 'watch_event_id'), as shown in row 50 onwards
watch_events_clean <- watch_events_clean %>%
  select(-impression_id)

# Cleaning of sessions
sessions_clean <- sessions %>%
  drop_na() %>%
  mutate(
    session_date = as.Date(login_at),
    watch_efficiency = ifelse(session_duration_sec > 0, (watch_seconds / session_duration_sec) * 100, 0)
  )

# Cleaning of impressions
# 1) Recoding the source labels to make more sense with the assignment
# Recode source labels to match project terminology
impressions_clean <- impressions_raw %>%
  mutate(
    source_bucket = recode(
      source_bucket,
      known = "followed",
      preferred_new = "recommended",
      explore = "explore"
    ),
    source_bucket = factor(source_bucket, levels = c("followed", "recommended", "explore"))
  ) %>%
  distinct(impression_id, .keep_all = TRUE)

# 2) Remove duplicated impressions
impressions_clean %>%
  count(impression_id) %>%
  filter(n > 1) %>%
  arrange(desc(n))

impressions_clean <- impressions_clean %>%
  distinct(impression_id, .keep_all = TRUE)

# 3) Standardize creator names for each creator_id
impressions_clean %>%
  distinct(creator_id, creator_display_name) %>%
  arrange(creator_id, creator_display_name) %>%
  filter(creator_id %in% (
    impressions_clean %>%
      distinct(creator_id, creator_display_name) %>%
      count(creator_id) %>%
      filter(n > 1) %>%
      pull(creator_id)
  ))

creator_name_map <- impressions_clean %>%
  mutate(
    creator_display_name_clean = creator_display_name %>%
      str_replace_all("-", " ") %>%
      str_remove_all("^(The\\s+)|(\\s+Official)$|(\\s+\\d+)$") %>%
      str_squish()
  ) %>%
  count(creator_id, creator_display_name_clean, sort = TRUE) %>%
  arrange(creator_id, desc(n), creator_display_name_clean) %>%
  group_by(creator_id) %>%
  slice(1) %>%
  ungroup() %>%
  select(creator_id, creator_display_name = creator_display_name_clean)

# Merge standardized creator names back into main dataset with a clear variable name
impressions_standardized <- impressions_clean %>%
  select(-creator_display_name) %>%
  left_join(creator_name_map, by = "creator_id")

## Creating of plots 

#Create an isolated output directory to avoid overwriting teammate artifacts
output_dir <- here("gen", "output", "impressions_analysis")
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

# Created plots

folders <- c(
  "gen/output/impressions_analysis",
  "gen/output/session_analysis",
  "gen/output/users_analysis",
  "gen/output/watch_event_analysis"
)
images <- unlist(lapply(folders, function(folder) {
  list.files(folder, pattern = "\\.png$", full.names = TRUE)
}))
knitr::include_graphics(images)

# Regression analysis, copy and paste from previous 

# Conclusion of regression 




```



## The analyses

## Regression analysis

This section examines whether users' content preferences are associated with the average number of videos they watch. First, we estimate a simple linear regression with gaming preference as the predictor. Then, we estimate a multiple linear regression including all of the content preference variables.

```{r loading_packages}

# Load packages needed for the regression analysis
if (!requireNamespace("RSQLite", quietly = TRUE)) install.packages("RSQLite")
if (!requireNamespace("DBI", quietly = TRUE)) install.packages("DBI")
if (!requireNamespace("tidyverse", quietly = TRUE)) install.packages("tidyverse")
if (!requireNamespace("here", quietly = TRUE)) install.packages("here")

library(RSQLite)
library(DBI)
library(tidyverse)
library(here)

```

```{r loading_data}
# Connect to the SQLite database
con <- dbConnect(SQLite(), dbname = here("tiktok_students.sqlite"))

# Get the relevant variables from the users table
users_regression <- dbGetQuery(con, "
  SELECT
    base_videos_watched_mean,
    pref_Comedy,
    pref_Dance,
    pref_BeautyFashion,
    pref_Food,
    pref_FitnessSports,
    pref_Gaming,
    pref_DIYHome,
    pref_Travel,
    pref_Education,
    pref_Pets
  FROM users
  WHERE
    base_videos_watched_mean IS NOT NULL
    AND pref_Comedy IS NOT NULL
    AND pref_Dance IS NOT NULL
    AND pref_BeautyFashion IS NOT NULL
    AND pref_Food IS NOT NULL
    AND pref_FitnessSports IS NOT NULL
    AND pref_Gaming IS NOT NULL
    AND pref_DIYHome IS NOT NULL
    AND pref_Travel IS NOT NULL
    AND pref_Education IS NOT NULL
    AND pref_Pets IS NOT NULL
") %>%
  as_tibble()

# Disconnect after the query is completed
dbDisconnect(con)
```

The dependent variable in this model is `base_videos_watched_mean` which is the average number of videos a user has watched. The independent variables are content preferences such as `pref_Gaming` and `pref_Travel`. First, we will run a simple regression model where we test whether a users' preference for gaming content is associated with the average amount of videos they have watched. 

```{r simple_regression}

  model_simple <- lm(
  base_videos_watched_mean ~ pref_Gaming,
  data = users_regression
)

summary(model_simple)
```
This shows a ??? relationship.

```{ r simple_regression_plot}
plot1 <- ggplot(users_regression, aes(x = pref_Gaming, y = base_videos_watched_mean)) +
  geom_point(alpha = 0.4, color = "pink") +
  geom_smooth(method = "lm", se = TRUE, color = "darkred") +
  labs(
    title = "Gaming preference and average videos watched",
    subtitle = "Simple linear regression",
    x = "Preference for gaming content",
    y = "Average number of videos watched"
  ) +
  theme_minimal()

plot1
```

The scatter plot shows the relationship between a users' preference for gaming content and the amount of videos they have watched. 

Now we will run a second model, including all the content preference variables. 

```{r multiple_regression}
model_multiple <- lm(
  base_videos_watched_mean ~ pref_Gaming +
    pref_Comedy +
    pref_Dance +
    pref_BeautyFashion +
    pref_Food +
    pref_FitnessSports +
    pref_DIYHome +
    pref_Travel +
    pref_Education +
    pref_Pets,
  data = users_regression
)

summary(model_multiple)
```

this shows....

```{r multiple_regression_plot, message=FALSE, warning=FALSE, fig.width=7, fig.height=4.5}
coef_df <- tibble(
  term = names(coef(model_multiple)),
  estimate = coef(model_multiple),
  conf.low = confint(model_multiple)[, 1],
  conf.high = confint(model_multiple)[, 2],
  p.value = summary(model_multiple)$coefficients[, 4]
) %>%
  filter(term != "(Intercept)")

plot2 <- ggplot(coef_df, aes(x = estimate, y = term)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_segment(
    aes(x = conf.low, xend = conf.high, y = term, yend = term),
    color = "darkred"
  ) +
  geom_point(size = 3, color = "pink") +
  labs(
    title = "Content preferences and average videos watched",
    subtitle = "Multiple linear regression coefficients with 95% confidence intervals",
    x = "Estimated effect on average videos watched",
    y = "Content preference"
  ) +
  theme_minimal()

plot2
```
this plot......
## Conclusion
